---
title: "wordshoal"
author: "Gustav Helms"
date: "11/8/2021"
output: html_document
---

```{r}
# loading packages
pacman::p_load(tidyverse, corpus)

# Installing the latest version of quanteda and wordshoal
devtools::install_github("https://github.com/quanteda/quanteda")
remotes::install_github("kbenoit/wordshoal")

# Loading the packages
library(quanteda)
library(wordshoal)
library(quanteda.textmodels)
```


```{r}
# Importing data
df <- read_csv("/Users/gustavhelms/Documents/Cognitive Science/5_semester/Bachelor/political_polarization/Folketinget-Scraping/data/folketinget_2019_2021_raw.csv")


# Subsetting to only five documents
subset <- df %>% filter(id == c("20201_M108_referat", "20201_M114_referat", 
                                "20201_M110_referat", "20201_M117_referat", "20201_M126_referat"))

```

# --------------------------------------------------------------------------------------------------------------
# Implementing the wordshoal function on our own data

```{r}
# Making the df into a corpus
corpus <- corpus(subset)


# Create a data frame matrix (dfm)
dfm <- dfm(tokens(corpus), remove_punct = TRUE)

# Fitting the model
wordshoalfit <- 
    textmodel_wordshoal(dfm, #dir = c(7,1), # I cannot figure out what the 'dir' argument does
                        groups = docvars(corpus, "id"), 
                        authors = docvars(corpus, "Name"))

# Inspecting the output
summary(wordshoalfit) 

```


```{r}
# Aggregating to get the positions of the mean positon of the parties
author_positions <- summary(wordshoalfit)$estimated.author.positions
author_positions$row_names <- rownames(author_positions)

fitdf <- merge(author_positions,
               docvars(corpus), 
               by.x = "row_names", by.y = "Name")
fitdf <- subset(fitdf, !duplicated(row_names))


aggregate(theta ~ Parti, data = fitdf, mean)
```


### The above example does not work. THe model only returns 0 values for the 'theta' (estimated position). There might be a problem with the conversion of the data frame into the dfm object. Cannot figure it out though.

# --------------------------------------------------------------------------------------------------------------

# The following example is the one provided in the documentation for the function. This one works. Maybe the answer is here somehow. 

```{r}
# Inspecting the data
summary(data_corpus_irish30)

```

```{r}
texts(corpus)[5]
```

```{r}
iedfm <- dfm(data_corpus_irish30, remove_punct = TRUE) 

wordshoalfit <- 
    textmodel_wordshoal(iedfm, dir = c(7,1),
                        groups = docvars(data_corpus_irish30, "debateID"), 
                        authors = docvars(data_corpus_irish30, "member.name"))

summary(wordshoalfit)                    

author_positions <- summary(wordshoalfit)$estimated.author.positions
author_positions$row_names <- rownames(author_positions)
fitdf <- merge(author_positions,
               docvars(data_corpus_irish30), 
               by.x = "row_names", by.y = "member.name")
fitdf <- subset(fitdf, !duplicated(memberID))
aggregate(theta ~ party.name, data = fitdf, mean)
```





